\ab{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}

### 2021-01-06 papers/intro_paper/intro_paper.tex
changes in title/abstract

\newcommand{\paperone}{Paper~I\xspace}
\newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}

@@

@@

\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}

\author{Abhirup Ghosh}
\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), D-14476 Potsdam-Golm, Germany}
\author{Richard Brito}
\affiliation{Dipartimento di Fisica, ``Sapienza" Universit`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185, Roma, Italy}
\author{Alessandra Buonanno}
\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), D-14476 Potsdam-Golm, Germany}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The no-hair conjecture in General Relativity states that the properties of a Kerr black hole (BH) are completely described by its mass and spin angular momentum. As a consequence, the complex quasi-normal-mode (QNM) frequencies of a binary black hole (BBH) ringdown can be uniquely determined by the mass and spin of the remnant object. Conversely, measurement of the QNM frequencies could be a independent test of the no-hair conjecture. This paper outlines a test of the no-hair conjecture by measuring the complex QNM frequencies of a BBH ringdown within the framework of, for the first time, a spinning inspiral-merger-ringdown waveform model, thereby using the entire signal power and removing dependency on the predicted or estimated start time of the proposed ringdown. We further demonstrate the robustness of the test against modified gravitational wave (GW) signals with a ringdown different from what GR predicts for Kerr BHs. The method was used to analyse the properties of the merger remnants for the events observed by LIGO-Virgo in the first half of their third observing run (O3a) in the latest LIGO-Virgo publication. In this paper, for the first time, we analyse the GW events from the first and second LIGO-Virgo observing runs and provide joint constraints with published results from O3a. We also analyse two events from the O3a list of events that were not considered for the initial analysis. Finally, the joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest constraints yet using this method. %Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\newcommand{\paperone}{Paper~I\xspace}
\newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
\newcommand{\ab}[1]{\textcolor{cyan}{#1}}
\newcommand{\comment}[1]{\textcolor{red}{[#1]}}

@@

\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}

@@

%\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}

\title{\ab{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}}

\author{Abhirup Ghosh}
\AEI
\author{Richard Brito}
\affiliation{Dipartimento di Fisica, ``Sapienza" Universit\`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185 Roma, Italia}
\author{Alessandra Buonanno}
\AEI
\UMD

@@

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  The no-hair conjecture in General Relativity states that the
  properties of an \ab{astrophysical} Kerr black hole (BH) are completely described by its
  mass and spin angular momentum. As a consequence, the complex
  quasi-normal-mode (QNM) frequencies of a binary black hole (BBH)
  ringdown can be uniquely determined by the mass and spin of the
  remnant object. Conversely, measurement of the QNM frequencies could
  be an independent test of the no-hair conjecture. This paper \ab{extends to spinning BHs earlier work} 
 \sout{outlines a} \ab{that proposed to} 
  test \sout{of} the no-hair conjecture by measuring the complex QNM
  frequencies of a BBH ringdown \sout{within the framework of, for the first
  time, a spinning} using inspiral-merger-ringdown waveform\ab{s} \sout{model}, thereby
  \sout{using} \ab{taking full advantage of} the entire signal power and removing dependency on the
  predicted or estimated start time of the proposed ringdown. We
  further demonstrate the robustness of the test against modified
  gravitational-wave (GW) signals with a ringdown different from what
  GR predicts for Kerr BHs. \ab{Our} method was used to analyse the
  properties of the merger remnants for the events observed by
  LIGO-Virgo in the first half of their third observing run (O3a) in
  the latest LIGO-Virgo publication. In this paper, for the first
  time, we analyse the GW events from the first \ab{(O1)} and second \ab{(O2)} LIGO-Virgo
  observing runs and provide joint constraints with published results
  from O3a. We also analyse two events from the O3a \ab{catalogue} \sout{list of events} 
  that were not considered \sout{for} \ab{in}  the initial \ab{LIGO-Virgo} analysis. Finally, the
  joint measurements of the fractional deviations in the frequency,
  $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
  constraints yet using this
  method. %Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%
